Appendix

### 2024-09-13 manuscript/manuscript_appendix.Rmd
Work on assessing the effect of normalisation prior to standardisation.

data <- .assess_standardisation_before_transformation()
```

>>>>

data <- .assess_standardisation_before_transformation()
data <- data[transformation %in% c("none", "conventional", "conventional (z-score norm.)", "conventional (robust scaling)", "invariant"), mget(c("residuals", "transformation", "dataset"))]
data[, "residuals" := round(residuals, digits = 1L)]
data.table::dcast(data, dataset ~ transformation, value.var = "residuals")
```
